Chum Populations

### 2015-08-07 paper/main.tex
figure for poster

\subsection*{Linkage map}
Here we present a consensus map placing XXX loci onto 37 linkage groups.  These 37 linkage groups correspond 1:1 with those reported in \citep{Waples2015} and likely have a 1:1 correspondence with the 37 chromosomes in chum salmon \citep{Phillips2001}. \textbf{Do we want a map figure, or just a table?}.

Overlap with population data.

A total of xxx paralogs were identified and placed onto the linkage map.  The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \textbf{few good citations here - Marine, Kodama, Waples, McKinney}. Consistency across families (see supplemental table xx)

>>>>

\subsection*{Linkage map}
Here we present a consensus map placing XXX loci onto 37 linkage groups.  These 37 linkage groups correspond 1:1 with those reported in \citep{Waples2015} and likely have a 1:1 correspondence with the 37 chromosomes in chum salmon \citep{Phillips2001}. \textbf{Do we want a map figure, perhaps just a slice of a single LG, or a table?}.

Of the xxx loci scored in wild collectionsm, xxx were placed on the linkage map, and covering all LGs.

A total of xxx paralogs were identified and placed onto the linkage map.  The location of these paralogs were were concentrated on the distal ends of three chromosomes, consistent with results found in other Salmonid species  \citep{Brieuc2014, Kodama2014, Waples2015} (also McKinney submitted). Consistency across families (see supplemental table xx)
